\LARGE \bf Multi-Camera Visual Servoing of a Flapping Wing Micro Air Vehicle

### 2012-09-11 manuscript.tex
Updated Flapping Wing MAV section.

\author{
    Ryan C. Julian$^{*}$,
    Cameron J. Rose$^{*}$,
    Humphrey Hu$^{\dagger}$, and
    Ronald S. Fearing$^{*}$
    \thanks{$^{*}$
    	R.C. Julian, C.J. Rose and R.S. Fearing are
        with the Department of Electrical Engineering and Computer Sciences,
        University of California, Berkeley, CA 94720 USA.
        \href{mailto:ryanjulian@berkeley.edu}{\tt ryanjulian@berkeley.edu},
        \href{mailto:c\_rose@eecs.berkeley.edu}{\tt c\_rose@eecs.berkeley.edu},
        \href{mailto:ronf@eecs.berkeley.edu}{\tt ronf@eecs.berkeley.edu}
    }
    \thanks{$^{\dagger}$
        H. Hu is with the Robotics Institute,
        Carnegie Mellon University, Pittsburgh, PA 15213 USA.
        \href{mailto:humphreh@andrew.cmu.edu.edu}{\tt humphreh@andrew.cmu.edu}
    }
%    \thanks{
%        This material is based upon work supported by the National Science
%        Foundation under Grants No. CNS-0931463 and IIS-0931463.
%    }
}

@@

%----------------------------------------------------------------------------%
\subsection{Flapping Wing Micro Air Vehicle}
%TODO(humphrey)
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed tincidunt erat et dolor commodo varius. Integer arcu metus, egestas vel tincidunt a, tincidunt quis massa. Aliquam sit amet felis nibh, in bibendum est. Ut augue tortor, elementum vel bibendum ac, faucibus at est. Etiam lacus libero, aliquet id eleifend vitae, sollicitudin et nunc. Sed condimentum, lacus nec ullamcorper vestibulum, elit quam eleifend augue, id iaculis est elit at tortor. Donec ac nulla tellus. Aenean viverra rhoncus odio a sagittis. Quisque gravida imperdiet lorem ut condimentum. Pellentesque eget quam dolor. Vestibulum a eros nisl, quis malesuada ipsum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum diam augue, ultrices et consectetur ut, fringilla egestas magna. Etiam consequat molestie massa, a pellentesque magna tincidunt non. Nullam aliquet augue et risus hendrerit facilisis.

>>>>

\author{
    Ryan C. Julian$^{*}$,
    Cameron J. Rose$^{*}$,
    Humphrey Hu$^{\dagger}$, and
    Ronald S. Fearing$^{*}$
    \thanks{$^{*}$
    	R.C. Julian, C.J. Rose and R.S. Fearing are
        with the Department of Electrical Engineering and Computer Sciences,
        University of California, Berkeley, CA 94720 USA.
        \href{mailto:ryanjulian@berkeley.edu}{\tt ryanjulian@berkeley.edu},
        \href{mailto:c\_rose@eecs.berkeley.edu}{\tt c\_rose@eecs.berkeley.edu},
        \href{mailto:ronf@eecs.berkeley.edu}{\tt ronf@eecs.berkeley.edu}
    }
    \thanks{$^{\dagger}$
        H. Hu is with the Robotics Institute,
        Carnegie Mellon University, Pittsburgh, PA 15213 USA.
        \href{mailto:humphreh@andrew.cmu.edu.edu}{\tt humphreh@andrew.cmu.edu}
    }
    \thanks{
        This material is based upon work supported by the National Science
        Foundation under Grants No. CNS-0931463, and by the Army Research
        Laboratory under the Micro Autonomous System and Technology
        Collaborative Technology Alliance.
    }
}

@@

%----------------------------------------------------------------------------%
\subsection{Flapping Wing Micro Air Vehicle}
%TODO(humphrey)
The flying platform used in this experiment is the H2Bird flapping wing MAV. It features a X-wing clap-fling flapping design, with a brushed DC motor powering the wings for propulsion and a tail propeller and servo-controlled tail elevator for control. Onboard electronics include a 40 MIPS microprocessor, 6 DoF IMU, 802.15.4 radio, VGA camera, and motor drivers powered by a 90 mAh lithium polymer battery. In routine flight, the H2Bird achieves [insert speed] m/s ground speed and can operate for approximately [10] minutes.
